Partitioned Local Depth (PaLD) Clustering Analyses in R

### 2022-05-23 r-journal/manuscript.Rmd
typo
update paper

---
title: "Partitioned Local Depth (PaLD) Clustering Analyses in R"
author:
  - name: Lucy D'Agostino McGowan
    affiliation: Wake Forest University
    address:
    - Winston-Salem, NC
    - 27106
    email:  mcgowald@wfu.edu
  - name: Katherine Moore
    affiliation: Wake Forest Unversity
    address:
    - Winston-Salem, NC
    - 27106
    email: mooreke@wfu.edu 
  - name: Kenneth Berenhaut 
    affiliation: Wake Forest University
    address:
    - Winston-Salem, NC
    - 27106
    email: berenhks@wfu.edu 
abstract: >
  An abstract of less than 150 words.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

@@

We present a new package, \CRANpkg{pald}, for calculating Partitioned Local Depths (PaLD) probabilities, implementing clustering analyses, and creating data visualizations to display community structure. This paper will describe how to use the package as well as walk through two examples.

>>>>

---
title: "Partitioned Local Depth (PaLD) Clustering Analyses in R"
author:
  - name: Lucy D'Agostino McGowan
    affiliation: Wake Forest University
    address:
    - Winston-Salem, NC
    - 27106
    email:  mcgowald@wfu.edu
  - name: Katherine Moore
    affiliation: Wake Forest Unversity
    address:
    - Winston-Salem, NC
    - 27106
    email: mooreke@wfu.edu 
  - name: Kenneth Berenhaut 
    affiliation: Wake Forest University
    address:
    - Winston-Salem, NC
    - 27106
    email: berenhks@wfu.edu 
abstract: >
  Partitioned Local Depths (PaLD) is a framework for a holistic consideration of the community structure of distance-based data. This paper describes an R package, \CRANpkg{pald}, for calculating Partitioned Local Depths (PaLD) probabilities, implementing clustering analyses, and creating data visualizations to display community structure. We describe how to use the package as well as walk through several examples. 
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

@@

We present a new package, \CRANpkg{pald}, for calculating Partitioned Local Depths (PaLD) probabilities, implementing clustering analyses, and creating data visualizations to display community structure. This paper will describe how to use the package as well as walk through several examples.

### 2022-05-23 r-journal/manuscript.tex
update paper

\abstract{%
An abstract of less than 150 words.
}

@@

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH 62fc4b4 UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from 62fc4b4 (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from 8ad41e8:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}

>>>>

\abstract{%
Partitioned Local Depths (PaLD) is a framework for a holistic
consideration of the community structure of distance-based data. This
paper describes an R package, \CRANpkg{pald}, for calculating
Partitioned Local Depths (PaLD) probabilities, implementing clustering
analyses, and creating data visualizations to display community
structure. We describe how to use the package as well as walk through
several examples.
}

@@

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH 8cc278d UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from 8cc278d (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from 7044f2e:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}
